### 2012-09-04 sections/conclusion.tex
* revision with professor's comments   * conclusion with a footnote to nfql source code (BSD licensed)

We presented \ac{NFQL}, an efficient C implementation of the stream-based flow
query language. The language allows applying absolute (or relative) filters,
aggregating flows into groups, evaluating timing relationships among them, and
merging them into one collection. \ac{NFQL} can execute such complex queries
in matter of minutes, thereby expanding the scope of current flow record
processing tools. The conducted performance evaluations reveal that \ac{NFQL}
is on par with tools that support only absolute filters. SiLK, the only openly
available package that provides tools that are similar to the rest of
\ac{NFQL}'s processing pipeline appears faster. This is because it can
optimize its operations in favor of the limited set of comparisons that are
only based on equality, and its usage of a different file storage format. The
evaluation queries developed as a part of this research work may also develop
into a more general benchmark suite for flow query tools and platforms.

>>>>

We presented
\ac{NFQL}\footnote{\texttt{\url{https://github.com/vbajpai/nfql}}}, an
efficient C implementation of the stream-based flow query language. The
language allows applying absolute (or relative) filters, aggregating flows
into groups, evaluating timing relationships among them, and merging them into
one collection. \ac{NFQL} can execute such complex queries in matter of
minutes, thereby expanding the scope of current flow record processing tools.
The conducted performance evaluations reveal that \ac{NFQL} is on par with
tools that support only absolute filters. SiLK, the only openly available
package that provides tools that are similar to the rest of \ac{NFQL}'s
processing pipeline appears faster. This is because it can optimize its
operations in favor of the limited set of comparisons that are only based on
equality, and its usage of a different file storage format. The evaluation
queries developed as a part of this research work may also develop into a more
general benchmark suite for flow query tools and platforms.
